String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-09 2023-1-19/sections/implementation.tex
experiments

\paragraph*{AutomatArk benchmark suite.}
The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraints. There are 8,751 instances in the AutomatArk suite.
Note that the original AutomatArk benchmark suite in \cite{z3str3re}  includes 19,979 instances, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}.

@@

We evaluated the performance of OSTRICH$^{\rm RECL}$ against the main-stream string constraint solvers, including CVC5 (version 1.0.5) \cite{cvc5}, Z3seq (version 4.8.9) \cite{z3seq}, Z3-Trau (github commit 1628747) \cite{z3trau}, Z3str3 (github commit 59e9c87) \cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH (github commit 8297d8d) \cite{atva2020}. All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory. We use the Zaligvinder framework \cite{zaligvinder_2021} to execute the experiments, where the timeout period is set as 60 seconds per instance.

>>>>

\paragraph*{AutomatArk benchmark suite.}
The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable). There are 8,751 instances in the AutomatArk suite.
Note that the original AutomatArk benchmark suite in \cite{z3str3re} include 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}. Only 8,751 ones out of 19,979 instances contain occurrences of counting operators.

@@

We evaluated the performance of OSTRICH$^{\rm RECL}$ against the state-of-the-art string constraint solvers, including CVC5 
%(version 1.0.5) 
\cite{cvc5}, Z3seq \cite{z3seq}, Z3-Trau 
%(github commit 1628747) 
\cite{z3trau}, Z3str3
%(github commit 59e9c87) 
\cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH\footnote{The name OSTRICH+ was used in~\cite{atva2020}, where nuXmv model checker was called to solve the nonemptiness of CEFA w.r.t. LIA. } 
%(github commit 8297d8d) 
\cite{atva2020}. All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory. We use the Zaligvinder framework \cite{zaligvinder_2021} to execute the experiments, where the timeout period is set as 60 seconds per instance.
